---
title: "Tikz Gallery"
author: "Prof. Walmes M. Zeviani"
output:
  html_document:
    css: style.css
    keep_md: true
    toc: true
    number_sections: false
---

```{r setup, include=FALSE}
opts_chunk$set(echo = FALSE,
               comment = NA,
               results = "asis",
               error = FALSE,
               warning = FALSE,
               message = FALSE)
a <- "```tex"
b <- "```"
```
```{r, include=FALSE}
file.remove("child.Rmd")
tmp <- readLines("template.Rmd")

pgf <- sub(x = list.files(path = "./src/", pattern = "*.pgf"),
           pattern = "\\.pgf$",
           replacement = "")
png <- sub(x = list.files(path = "./src/", pattern = "*.png"),
           pattern = "\\.png$",
           replacement = "")

# Lista de arquivos que tem os pares pgf e png.
i <- intersect(pgf, png)
sapply(i,
       FUN = function(i){
           tmpi <- gsub(x = tmp,
                        pattern = "&PGF_FILE&",
                        replacement = i)
           cat(tmpi,
               file = "child.Rmd",
               append = TRUE,
               sep= "\n")
       })
```

This is my collection, or gallery, of Tikz Art.  The official Tikz
Gallery is on [TeXample.net](http://www.texample.net/tikz/examples/). A
interesting exposition of Tikz features is done in
<http://tug.ctan.org/info/visualtikz/VisualTikZ.pdf>. The official
manual is available at
<http://linorg.usp.br/CTAN/graphics/pgf/base/doc/pgfmanual.pdf>.

There are `r length(i)` Tikz figures in this gallery.  Most of them were
done to teach statistics, inspired by content on the web or done from
the scratch.  Also, a lot were caught in the web and copied with few
modifications (I run tests on it).

I use [ktikz editor](https://apps.ubuntu.com/cat/applications/ktikz/) to
edit these Tikz files.

This repository is maintained in to Git Version Control and is hosted on
[GitHub](https://github.com/walmes/Tikz).

If you want to reproduce these figures, do not forget of seeing the
corresponding preamble that list all tikz libraries used:
[TIKZ_PREAMBLE.pgs](https://github.com/walmes/Tikz/blob/master/src/TIKZ_PREAMBLE.pgs).

The figures are in file file order.  A page with all figures displayed
in on <http://www.leg.ufpr.br/~walmes/Tikz/> (updated less frequently).

Some useful tutorials or galleries:

  * <https://tobiw.de/en/teotm/tikz-adventskalender>.
  * <http://math.et.info.free.fr/TikZ/bdd/TikZ-Impatient.pdf>.
  * <http://www.mat.ufpb.br/lenimar/introtikz.pdf>.

```{r, child = "child.Rmd"}
```
