---
title: "Tikz Gallery"
author: "Prof. Walmes M. Zeviani"
output:
  html_document:
    css: style.css
    keep_md: true
    toc: true
    number_sections: false
---

```{r setup, include=FALSE}
opts_chunk$set(
    echo=FALSE, comment=NA, results="asis",
    error=FALSE, warning=FALSE, message=FALSE
)
a <- "```tex"
b <- "```"
```
```{r, include=FALSE}
file.remove("child.Rmd")
tmp <- readLines("template.Rmd")

pgf <- sub(x = list.files(path = "./src/", pattern = "*.pgf"),
           pattern = "\\.pgf$", replacement = "")
png <- sub(x = list.files(path = "./src/", pattern = "*.png"),
           pattern = "\\.png$", replacement = "")

## Lista de arquivos que tem os pares pgf e png.
i <- intersect(pgf, png)
sapply(i,
       FUN = function(i){
           tmpi <- gsub(x = tmp, pattern = "&PGF_FILE&",
                        replacement = i)
           cat(tmpi, file = "child.Rmd",
               append = TRUE, sep= "\n")
       })
```

This is my collection, or gallery, of Tikz Art.  The official Tikz
Gallery is on [TeXample.net](http://www.texample.net/tikz/examples/).

There are `r length(i)` Tikz figures in this gallery.  Most of them were
done to teach statistics, inspired by content on the web or done from
the zero.  Also, a lot were catch in the web and copied with few
modifications.

To build them, I use
[ktikz editor](https://apps.ubuntu.com/cat/applications/ktikz/).

To the sake of accessibility and security, this repository is maintained
in to git services: 1) officially in my profile on
[GitHub](https://github.com/walmes/Tikz) and 2) mirrored in the
[GitLab](http://git.leg.ufpr.br/walmes/Tikz) of my laboratory.

If you want to reproduce these figures, do not forget of seeing the
corresponding preamble that list all tikz libraries used:

  * GitHub:
    [TIKZ_PREAMBLE.pgs](https://github.com/walmes/Tikz/blob/master/src/TIKZ_PREAMBLE.pgs);
  * GitLab:
    [TIKZ_PREAMBLE.pgs](http://git.leg.ufpr.br/walmes/Tikz/blob/master/src/TIKZ_PREAMBLE.pgs).

The figures are in alphabetic order. A page with all figures displayed
in on <http://www.leg.ufpr.br/~walmes/tikz/>.

```{r, child="child.Rmd"}
```
